Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-09 main.tex
rough draft for first part of intro

    %%% CONTEXT %%%
    \begin{itemize}
      \item What is a scientific workflow?
      \item Scientific workflows are all over the place $\rightarrow$ important!
      \item Scheduling (order, maybe even concrete starting times) is important for efficient workflow executions
      \item Only mapping tasks to processors is not enough.
      \item This also allows to reuse processors, which is important to achieve good HW utilization / makespans (explain!).
    \end{itemize}

>>>>

    %%% CONTEXT %%%
    Data analysis on massive data sets (stemming from areas such as genomics, 
    remote sensing, or biomedical imaging -- to name just a few) has become ubiquitous in science;
    it often happens in the form of workflows, \iec separate software components chained together
    in some kind of complex pipeline~\cite{DBLP:journals/dbsk/LeserHDEGHKKKKK21}.
    Such workflows are usually represented as directed acyclic graphs (DAGs).
    The DAG vertices represent the software components (more general: the workflow \emph{tasks}),
    while the edges model I/O dependencies between the tasks~\cite{adhikari2019survey,liuPacitti}.
    Large workflows with resource-hungry tasks can easily exhaust the capabilities of a 
    single computer and are thus executed on a parallel or distributed platform.
    An efficient execution of the workflows on such platforms requires not only to map the tasks
    to a particular processor, but also a good task schedule, \iec an execution order
    and possibly also starting times for the tasks.

    \begin{itemize}
      \item This also allows to reuse processors, which is important to achieve good HW utilization / makespans (explain!).
    \end{itemize}
